\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-29 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

        From this, we can deduce the confidence interval $CI^{ref}_{is} = \hat{\beta}_{is}^{max,ref} - \hat{\beta}_{is}^{min,ref}$.

        \item  Our method provides estimates of the underlying trade costs components ($\widehat{\tau}_i$, $\widehat{\tau}_s$, $\widehat{t}_i$, $\widehat{t}_s$) with an associated matrix of variance-covariance, from which we can rebuild $\beta_{is}$ (on a year-transport mode basis). As such, it does not yield an estimate of $\beta_{is}$ and an associated standard deviation, so that we cannot directly compare the precision of the estimation. We then deduce the accuracy of the $\beta$ estimate by relying on bootstrap method. Specifically, on a yearly/mode basis we draw a distribution of trade costs components and associated $\beta_{is}$ (10,000 random draws) from which we can compute the mean, the median and the 5-95 threshold values for each couple $i,s$. Noticing $\beta_{is}^{95}$ and $\beta_{is}^{05}$ the associated thresholds, we then obtain the confidence interval $CI_{is}= \beta_{is}^{95}- \beta_{is}^{05}$.\footnote{Notice that this should be made on the same sample as the one obtained with the referee's method, since the goal is to compare the accuracy of the $\beta_{is}$ estimate - implying to have the same sample of countries / sectors at first. }

    \item We can then evaluate the accuracy of each estimation method by comparing the size of the confidence intervals of the $\beta$, for each couple $i,s$ (by year and transport mode). We summarize this comparison in Figure \ref{fig:accuracy_beta}, which reports the distribution of the ratio of confidence intervals, taken in log.\textbf{XXX CETTE FIGURE, SUR QUELLE ANNEE, QUEL MODE DE TRANSPORT? xxxxx}

    \begin{figure}[htbp]
    \caption{Accuracy of the estimation of the $\beta$: Comparison}
    \label{fig:accuracy_beta}
    \begin{center}
    \includegraphics[height=4in]{../../revised_article/comparaison_amplitude_baseline_referee1_2013_ves.png"}
    \begin{minipage} [c]  {5in} \scriptsize%
    	    Note: Ratio of the confidence intervals = $ _{}ln(CI_{is}/CI^{ref}_{is})$
    \end{minipage}

    \end{center}
    \end{figure}

   \textbf{XXXX J’ai laissé en plan le calcul sur d’autres modes et d’autres années à reprendre ? commit 16b215ca44c3f4cfb0fd43d3aaec6e6532aa7f9d  GD} In most cases, the log of the ratio is negative, implying a lower interval confidence of the $\beta$ estimate with our methodology. Our method undoubtedly yields more accurate estimations of the share of additive components, whatever the transport mode considered. We have checked that a similar conclusion applies on other years (they are not reported here for sake of brevity but they are available upon request).
    \end{itemize}

@@

\subsection{Critique 2: Calculation of Unit Prices}

\textit{My second critique concerns the way the authors are calculating the unit prices.
The Census data reports the quantity of goods per observation. So, the authors
can calculate the unit price as Value/Quantity, which is consistent with how
price is modeled in standard trade models. Instead, the authors calculate unit
price as Value/Weight. This used to be a common exercise in the past where
many data-sets did not report Quantity. But, given their data, there is no
justification for the authors to calculate the prices this way.}

\textit{Calculating the unit price as Value/Weight presents the authors
with an additional endogeneity problem. To elaborate, let $\omega_{ik} = Weight/Quantity$
denote the unit weight of the goods in observation $ik$. [...] There is evidence that (i) $\omega_{ik}$ varies significantly within narrowly-defined product
categories, and (ii) $\omega_{ik}$ is negatively correlated with transport costs. So the
way the authors are calculating unit prices and estimating the model creates a
new (but avoidable) source of endogeneity.}

% MEMO: DO NOT FORGET TO REPORT THE ARGUMENTATION BELOW IN THE MAIN TEXT XXX
\paragraph{Our answer:}
\noindent This is a very important point we had not thought about, and we thank the referee for raising it.
The referee definitely has a point here, in the sense that Census data do report the quantity of goods (and sometimes even two quantities).
%At a more fundamental level, this raises the following question: Do we have reason to believe our measure of unit prices generate significant deviations from the one relying on quantities?
To that extent, the findings by \cite{Lashkaripour_JIE2020} were an eye-opener.
Based on US data very similar to ours over the period 1995-2015, the paper highlights, among other results, that the unit weight of imported goods is indeed substantially heterogeneous even within narrowly-defined product categories and the cost of transportation increases more rapidly with unit weight than the cost of production.  \cite{Lashkaripour_JIE2020} finds that accounting for the heterogeneity in export unit weights provides evidence in favor of the iceberg cost assumption regarding transport costs.
This result of transport costs close to be totally iceberg contrasts from our own findings of additive costs representing 30 to 45\% of total costs.
We believe the two sets of findings are complementary.

We now report results based on per-unit prices.
They confirm the results of \cite{Lashkaripour_JIE2020}
Yet, first, looking at per-unit prices leads to leaving aside a large part of the data, both sectorally and chronologically.
Second  it is interesting to look at additive costs on a per-weight basis even there is a correlation between unit price and weight.

%The two stories are not necessarily incompatible, however.
Beyond a longer time span, our database is exhaustive, and encompasses all goods and industries, while \citet{Lashkaripour_JIE2020}) restricts to indivisible/discrete goods representing a bit more 56\% of US total imports of goods. In this regard, when comparing Tables 1 and 10 in \citet{Lashkaripour_JIE2020}, one can see that the share of multiplicative costs tends to decrease with the share of discrete goods. It is therefore reasonable to think that the inclusion of all goods, like in our setting, would move the average share of multiplicative costs far from 100\%.

%Nevertheless, the point made by the referee is an important one and deserves careful investigation. We devoted a lot of thought to a potential switch from weight to quantity.
%Running the estimation considering quantities (i.e., units) rather than weight, still on the transport mode-yearly basis yet appears really uneasy in our context for several, non-trivial reasons, that we develop below.

\subsubsection{Data issues}

We do not know why that is, but the Census Bureau data do not report quantities by transport mode.
Nor do the 1974-2004 Hummels’s data, which is based on the Census Bureau data. 
This is incompatible with our empirical strategy of estimation transport costs which is conditional on the transport mode, similarly as in \cite{hummels2007}.
As a result, to compute the unit price of all trade would require the assumption that the weight per unit is the same for vessel shipments and air shipments at the level of the observation.
This is unlikely, as one would expect the higher-to-weight value to be transported by air rather than by vessel.
Hummels data are reported at the  sitc rev2 5-digit x  country level. In that context, 41.1 \% of trade flows and 79\% of trade value are multimode.
Reducing the total value of the sample from 12,500 billion dollars to 2,650 billion dollars would entail of large loss of useful information. 
%data from "vérification quantities.do"
Original census data, when accessible (normally from 1989, but actually only for 1997-1999 and from 2002 because of the Covid situation), are more promising.
They are reported at the HS-10 digit x district of entry x district of unleading x rate provision code.
In 2019, multi-modal flows are 570 billion dollars out of 1,790 billion dollars, or 31\% of the data.
This is still a large share, but not too large to perclude any work. 
So we decided to work only with data obtained directly from the Bureau of census.

%This would be a non-trivial reduction.  for Hummels). We could restrict observations to single-mode flows, but that would alter our sample in a non-trivial way, raising some potential selection biases. Investigating this possibility shows that this would reduce the total value of trade flows from around 32,000 billion dollars, to 7,000 billion dollars, i.e. a reduction of flows by a factor of 4.5. \textbf{XXX LP: Donne l'impression que ce n'est pas ce qu'on fait, alors que si, en fait? XXX}

%Even on this very reduced sample
Another difficulty is that our data, comming from Hummels or the Bureau of Census, include quantity, but not units.
To the best of our knowledge, these can only be found in the "Harmonized Tariff Schedule of the United State".
These schedules change many time per year.
Schedules from 1987 can be found on the webside of the bureau (https://www.usitc.gov/tata/hts/archive/index.htm), but the ones from 1987 to 2008 are under pdf or html format.
We could only find them in .csv format in a continuous manner from 2009.
Even these files need cleaning up as the units are not always coherent (eg weight can be given in "kg" "kg." "Kg" and, also, "g" and "t").
We did not try to transform the older pdf and html ones into csv, as that would have been too much work compared to our objectives.
This is important, because, at our sector level (3-digit  sitc rev2 ), goods (either 5-digit sitc rev 2 or 10-digit hts) are measured in different units.
In 2019, only 125 3-digit sitc sectors out of 230 are measured in a single unit (after cleaning up the unit names).
For example, 3-digit sitc sector "061. Sugar, molasses and honey" includes among other products, 5-digit sitc "06150 Molasses, whether or not decolourized", measured in liters and 5-digit sitc "06160 Natural Honey" measured in kg.
Actually worse than this, the 5-digit sitc product "06190 Other sugars; sugar syrups; artificial honey (whether or not mixed with natural honey); caramel" includes both 10-digit hts product "1702903500 Other: invert molasses", measured in liters and 10-digit hts product " 1702602200 Blended syrups described in additional u.s. note 4 to chapter 17: described in general note 15 of the tariff schedule and entered pursuant to its provisions"  measured in kilograms.
3-digit sitc sector "291 Crude animal materials, n.e.s." includes 5-digit sitc products measured in kg ("29250 Seeds, fruit and spores, n.e.s., of a. kind used for sowing), in pieces ("29269 Other live plants (including trees, shrubs, bushes, roots, cuttings and slips)" )or measured in kg or not measured at all ("29230 Vegetable materials of a. kind used primarily for plaiting (e.g. cereal straw, cleaned, bleached or dyed, osier, reeds, rushes, rattans, bamboos, raffia and lime bark").

So we are limited to using quantity units from 2009 to 2019.
hese have to be found information on the \textit{units} considered for \textit{quantities} are not available for many years over our period, especially in the 1970s and the 1980s; discarding information on this would lead to blurred results as many types of units can be found within a same sector (dozens, liters, etc...) which are hardly comparable with each other. The option of not considering these observations would mean a drastic reduction in the estimation period that could be covered. Again, this is particularly problematic considering that the time length is crucial for the assessment of transport costs long-run dynamics, which is one of the main objectives of the paper. \textbf{XXXX LP: Je ne suis pas sure de cet argument. Veut-on dire que dans les "quantity", en fait on trouve de tout mais pas des unites? Je crois que je comprends, check with Guillaume }

### 2021-10-29 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

\subsection{Critique 2: Calculation of Unit Prices}

\textit{My second critique concerns the way the authors are calculating the unit prices.
The Census data reports the quantity of goods per observation. So, the authors
can calculate the unit price as Value/Quantity, which is consistent with how
price is modeled in standard trade models. Instead, the authors calculate unit
price as Value/Weight. This used to be a common exercise in the past where
many data-sets did not report Quantity. But, given their data, there is no
justification for the authors to calculate the prices this way.}

\textit{Calculating the unit price as Value/Weight presents the authors
with an additional endogeneity problem. To elaborate, let $\omega_{ik} = Weight/Quantity$
denote the unit weight of the goods in observation $ik$. [...] There is evidence that (i) $\omega_{ik}$ varies significantly within narrowly-defined product
categories, and (ii) $\omega_{ik}$ is negatively correlated with transport costs. So the
way the authors are calculating unit prices and estimating the model creates a
new (but avoidable) source of endogeneity.}

% MEMO: DO NOT FORGET TO REPORT THE ARGUMENTATION BELOW IN THE MAIN TEXT XXX
\paragraph{Our answer:}
\noindent This is a very important point we had not thought about, and we thank the referee for raising it.
The referee definitely has a point here, in the sense that Census data do report the quantity of goods (and sometimes even two quantities).
%At a more fundamental level, this raises the following question: Do we have reason to believe our measure of unit prices generate significant deviations from the one relying on quantities?
To that extent, the findings in \cite{Lashkaripour_JIE2020} were an eye-opener.
Based on US data very similar to ours over the period 1995-2015, the paper highlights, among other results, that the unit weight of imported goods is indeed substantially heterogeneous even within narrowly-defined product categories and the cost of transportation increases more rapidly with unit weight than the cost of production.  \cite{Lashkaripour_JIE2020} finds that accounting for the heterogeneity in export unit weights provides evidence in favor of the iceberg cost assumption regarding transport costs.
This result of transport costs close to be totally iceberg contrasts from our own findings of additive costs representing 30 to 45\% of total costs.
We believe the two sets of findings are complementary.

@@

We do not know why that is, but the Census Bureau data do not report quantities by transport mode.
Nor do the 1974-2004 Hummels’s data, which is based on the Census Bureau data. 
This is incompatible with our empirical strategy of estimation transport costs which is conditional on the transport mode, similarly as in \cite{hummels2007}.
As a result, to compute the unit price of all trade would require the assumption that the weight per unit is the same for vessel shipments and air shipments at the level of the observation.
This is unlikely, as one would expect the higher-to-weight value to be transported by air rather than by vessel.
Hummels data are reported at the  sitc rev2 5-digit x  country level. In that context, 41.1 \% of trade flows and 79\% of trade value are multimode.
Reducing the total value of the sample from 12,500 billion dollars to 2,650 billion dollars would entail of large loss of useful information. 
%data from "vérification quantities.do"
Original census data, when accessible (normally from 1989, but actually only for 1997-1999 and from 2002 because of the Covid situation), are more promising.
They are reported at the HS-10 digit x district of entry x district of unleading x rate provision code.
In 2019, multi-modal flows are 570 billion dollars out of 1,790 billion dollars, or 31\% of the data.
This is still a large share, but not too large to perclude any work. 
So we decided to work only with data obtained directly from the Bureau of census.

%This would be a non-trivial reduction.  for Hummels). We could restrict observations to single-mode flows, but that would alter our sample in a non-trivial way, raising some potential selection biases. Investigating this possibility shows that this would reduce the total value of trade flows from around 32,000 billion dollars, to 7,000 billion dollars, i.e. a reduction of flows by a factor of 4.5. \textbf{XXX LP: Donne l'impression que ce n'est pas ce qu'on fait, alors que si, en fait? XXX}

%Even on this very reduced sample
Another difficulty is that our data, comming from Hummels or the Bureau of Census, include quantity, but not units.
To the best of our knowledge, these can only be found in the "Harmonized Tariff Schedule of the United State".
These schedules change many time per year.
Schedules from 1987 can be found on the webside of the bureau (https://www.usitc.gov/tata/hts/archive/index.htm), but the ones from 1987 to 2008 are under pdf or html format.
We could only find them in .csv format in a continuous manner from 2009.
Even these files need cleaning up as the units are not always coherent (eg weight can be given in ``kg’’, ``kg." ``Kg" and, also, ``g" and ``t").
We did not try to transform the older pdf and html ones into csv, as that would have been too much work compared to our objectives.
This is important, because, at our sector level (3-digit  sitc rev2 ), goods (either 5-digit sitc rev 2 or 10-digit hts) are measured in different units.
In 2019, only 125 3-digit sitc sectors out of 230 are measured in a single unit (after cleaning up the unit names).
For example, 3-digit sitc sector ``061 Sugar, molasses and honey" includes among other products, 5-digit sitc product ``6150 Molasses, whether or not decolourized", measured in liters and 5-digit sitc product ``06160 Natural Honey" measured in kg.
Actually worse than this, the 5-digit sitc product ``06190 Other sugars; sugar syrups; artificial honey (whether or not mixed with natural honey); caramel" includes both 10-digit hts product ````1702903500 Other: invert molasses", measured in liters and 10-digit hts product ``1702602200 Blended syrups described in additional u.s. note 4 to chapter 17: described in general note 15 of the tariff schedule and entered pursuant to its provisions"  measured in kilograms.
3-digit sitc sector ``291 Crude animal materials, n.e.s." includes 5-digit sitc products measured in kg (``29250 Seeds, fruit and spores, n.e.s., of a. kind used for sowing), in pieces (``29269 Other live plants (including trees, shrubs, bushes, roots, cuttings and slips)" )or measured in kg or not measured at all (``29230 Vegetable materials of a kind used primarily for plaiting (e.g. cereal straw, cleaned, bleached or dyed, osier, reeds, rushes, rattans, bamboos, raffia and lime bark").
Neglecting these differences would invalidate our functional forms, as no one expects the transport cost of a ``piece" to be the same as the transport cost of a ``kg’’, even in the same sector.
So we are limited to using quantity units from 2009 to 2019.

%
%hese have to be found information on the \textit{units} considered for \textit{quantities} are not available for many years over our period, especially in the 1970s and the 1980s; discarding information on this would lead to blurred results as many types of units can be found within a same sector (dozens, liters, etc...) which are hardly comparable with each other. The option of not considering these observations would mean a drastic reduction in the estimation period that could be covered. Again, this is particularly problematic considering that the time length is crucial for the assessment of transport costs long-run dynamics, which is one of the main objectives of the paper. \textbf{XXXX LP: Je ne suis pas sure de cet argument. Veut-on dire que dans les "quantity", en fait on trouve de tout mais pas des unites? Je crois que je comprends, check with Guillaume }
%
%\textbf{SUPPRIMER CE QUI EST EN GRAS Time length is especially important considering that, in the 1970s, trade composition was significantly different from today, with more goods for which correlation between weight and quality is likely to be less obvious} \textbf{XXX GUILLAUME: EXAMPLES XXX}. 
%
%
%Considering the US census data which complete the original \cites{hummels2007} database, it is true that we can retrieve information on quantities. Specifically, this can be obtained crossing HS-10 product information with the correspondence table between the HS-6 product classification and the associated units (kg, tons, liters, numbers, etc.) also provided by the US Census. We are able to collect information since 2009. Investigating this database, it appears that in many 3-digit sectors, there are more than one type of quantities reported (for instance, sector \textbf{XXX} includes goods both recorded in terms of \textbf{YYY} and \textbf{ZZZ}.) To identify a proper unit price, we consequently reduce the flows to the 3-digit sectors reporting a single quantity \textbf{at the 3-digit level}.

The same issue imposes the use of (sector,quantity unit) fixed effect rather than sector fixed effects
But this is not enough to adapt our equation to unit prices rather than weight price.
As discussed above, in our baseline regression we separate each transport cost component in its two distinct sector-origin country dimensions.
As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector.
In the specific case of quantities, this raises a non-trivial issue for country-level fixed effects.
Sector-level fixed effects can be easily replaced by (sector,quantity unit) fixed effects.
But the same is not possible for country fixed effects.
In the per-weight price, the existence of a single country fixed effect applicable to all sector could be justified, as a kilogram is always a kilogram and one can assume they both add the same to transport from, say, Germany.
But a unit of tee-shirt is quite different from an unit of car.
Assume imports of tee-shirts and cars from Germany and China.
Importing a tee-shirt from either country implies paying the fixed effect for both countries (the same for all sectors) and the fixed effect for the sector (the same for all countries).
Idem for importing a car.
Hence, the difference in the cost of importing a car from Germany and the cost of importing a car from China would be the same (in dollars) as difference between the cost of importing a tee-shirt from Germany and the cost of importing a tee-shirt from China.
This does not seem to us as a reasonable assumption; in this case specifically, we cannot keep the separability assumption.
As discussed before, that dramatically increases the computational difficulty of our method and yet does not yield different results.
